Git Learning Notes

### 2015-02-05 ch-intro/ch-intro.tex
main text fine tuned

\begin{figure}[htb]
\centering
\includegraphics[width=0.5\textwidth]{blackbody1}
\caption[Spectral radiance of blackbody at 0, 50 and 100 \si{\degreeCelsius} predicated by Planck's Law]{Spectral radiance of blackbody at 0, 50 and 100 \si{\degreeCelsius} predicated by Planck's Law.}
\label{fig:introbb}
\end{figure}

@@

Photocatalytic activity occurs when a semiconductor in aqueous solution is illuminated by photons of energy larger than the bandgap, then the carriers (electron and hole) drift and generate free radicals, i.e., \ce{OH.}, which enable further reactions. For photochemical water reduction to occur, the flat-band potential of the semiconductor (for highly doped semiconductors, this equals to the bottom of the conductance band) must exceed the proton reduction potential of 0.0 V vs NHE at pH 0. Flat-band potentials strongly depend on ion absorption (protonation of surface hydroxyl groups), crystallographic orientation of the exposed surface, surface defects, and surface oxidation processes.\cite{Osterloh2008} For water splitting using solar energy, the bandgap should be within $2.0 \sim 3.0 $ eV, and \gls{cb} edge should be more negative than reduction potential of \ce{H^+/H2}, whereas the \gls{vb} top should be more positive than the oxidation potential of \ce{H2O}/\ce{O2}.\cite{Osterloh2008,Wang2012} The valence band holes (\ce{h^+}) oxidize water to oxygen and conduction band electrons propel hydrogen generation, as depicted in Eq.~\ref{eq:h2o}.
\begin{subequations}\label{eq:h2o}
\begin{align}
4\ce{h^+} +  \ce{H2O} &\rightarrow \ce{O2} + 4\ce{H^+} \label{eq:hervb}\\
4\ce{H^+} +  4e^- &\rightarrow 2\ce{H2} \label{eq:hercb}
\end{align}
\end{subequations}
As shown in Fig.~\ref{fig:woxnhe}, \ce{WO3} has \gls{cb} edge positioned slightly more positive than reduction potential of \ce{H^+/H2} versus \gls{nhe}, and \gls{vb} edge much more positive than the oxidation potential of \ce{H2O}/\ce{O2}. So the photo-cleavage of water cannot be accomplished by \ce{WO3} alone. Nevertheless, a tandem cell approach by \ce{WO3} film and dye-sensitized \ce{TiO2} has been demonstrated with an efficiency of 4.5\%.\cite{Michael1999} It is worth noting that green plants also have two photosynthetic systems connected in series, one for oxidation of water into oxygen and the other for fixation of carbon dioxide.
% wo3 vs NHE
\begin{figure}[htb]
\centering
\includegraphics[width=0.6\textwidth]{woxnhe.jpg}
\caption[Band position of \ce{WO3} versus NHE]{Band position of \ce{WO3} in contact with aqueous electrolyte at pH 1. Reproduced from Ref.\cite{Gratzel2001}}
\label{fig:woxnhe}
\end{figure}
Moreover, favorable oxygen evolution of \ce{WO3} brings good performance in degradation of organic compounds.\cite{Hepel2001,Luo2001,Watcharenwong2008} The formation of long-lived holes is recognized as a key requirement.\cite{Pesci2011} Besides, \ce{WO3} is remarkably stable in acid, making it a significant candidate for treating water pollutant caused by organic acids.\cite{Monllor-Satoca2006}

>>>>

\begin{figure}[htb]
\centering
\includegraphics[width=0.5\textwidth]{blackbody1.pdf}
\caption[Spectral radiance of blackbody at 0, 50 and 100 \si{\degreeCelsius} predicated by Planck's Law]{Spectral radiance of blackbody at 0, 50 and 100 \si{\degreeCelsius} predicated by Planck's Law.}
\label{fig:introbb}
\end{figure}

@@

Photocatalytic activity occurs at the semiconductor-electrolyte interface where charge carriers (electrons or holes) are produced in a semiconductor illuminated by photons of energy exceeding that of the band gap, then drift and generate free radicals, i.e. \ce{OH.}, enabling further reactions. A much desired goal is water splitting using photocatalytic activity from solar energy. Semiconductor is in the center of photoelectrochemical cell design for water splitting, e.g. the band gap should be within $2.0 \sim 3.0 $ eV, and \gls{cb} edge should be more negative than reduction potential of \ce{H^+/H2}, whereas the \gls{vb} top should be more positive than the oxidation potential of \ce{H2O}/\ce{O2}.\cite{Osterloh2008,Wang2012} The valence band holes (\ce{h^+}) oxidize water to oxygen and conduction band electrons propel hydrogen generation, as depicted in Eq.~\ref{eq:h2o}.
\begin{subequations}\label{eq:h2o}
\begin{align}
4\ce{h^+} +  \ce{H2O} &\rightarrow \ce{O2} + 4\ce{H^+} \label{eq:hervb}\\
4\ce{H^+} +  4e^- &\rightarrow 2\ce{H2} \label{eq:hercb}
\end{align}
\end{subequations}

% wo3 vs NHE
\begin{figure}[htb]
\centering
\includegraphics[width=0.6\textwidth]{woxnhe.jpg}
\caption[Band position of \ce{WO3} versus NHE]{Band position of \ce{WO3} in contact with aqueous electrolyte at pH 1. Reproduced from Ref.\cite{Gratzel2001}}
\label{fig:woxnhe}
\end{figure}
As shown in Fig.~\ref{fig:woxnhe}, \ce{WO3} has \gls{cb} edge positioned slightly more positive than reduction potential of \ce{H^+/H2} versus \gls{nhe}, and \gls{vb} edge much more positive than the oxidation potential of \ce{H2O}/\ce{O2}. So the photo-cleavage of water cannot be accomplished by \ce{WO3} alone. Nevertheless, a tandem cell approach by \ce{WO3} film and dye-sensitized \ce{TiO2} has been demonstrated with an efficiency of 4.5\%.\cite{Michael1999} It is worth noting that green plants also have two photosynthetic systems connected in series, one for oxidation of water into oxygen and the other for fixation of carbon dioxide. Moreover, favorable oxygen evolution of \ce{WO3} brings good performance in degradation of organic compounds.\cite{Hepel2001,Luo2001,Watcharenwong2008} The formation of long-lived holes is recognized as a key requirement.\cite{Pesci2011} Besides, \ce{WO3} is remarkably stable in acid (pH $<5$), making it a significant candidate for treating water pollutant caused by organic acids.\cite{Monllor-Satoca2006}

### 2015-02-05 ch-moox/moox.tex
images replaced, fine tune
main text fine tuned

As shown in Fig.~\ref{fig:mooxch}, the crystal structure and phase of the as-synthesized specimen were examined by XRD and Raman. The XRD pattern (Fig.~\ref{fig:moxrd}) is readily indexed to the orthorhombic phase of \ce{MoO3} (ICDD PDF 05-0508, \emph{a}=3.9628 \AA, \emph{b}=13.855 \AA, \emph{c}=3.6964 \AA). The space group is $D_{2h}^{16}(Pbnm)$. This crystal structure is indeed a unique example among transition metal oxides, representing a transitional stage between tetrahedra and octahedral coordination.\cite{Itoh2001a} The strongest peak index is (110), suggesting the orientation of \ce{MoO3} is not parallel to the substrate, which is consistent with the morphology displayed in Fig.~\ref{fig:mosem1}. In contrast, a different XRD peak pattern is observed in Sec.~\ref{sec:nasi}, where the catalytic growth occurs.
% xrd raman
\begin{figure}[htb]
\centering
\subfloat[]{\label{fig:moxrd}\includegraphics[width=0.45\textwidth]{xrd_moo3}}\hspace{0.04\textwidth}
\subfloat[]{\label{fig:moram}\includegraphics[width=0.45\textwidth]{raman_moo3}}
\caption[Crystalline phase characterization of \ce{MoO3} on Si]{Crystalline phase characterization of \ce{MoO3} on Si: (a) XRD pattern and (b) Raman spectrum of typical \ce{MoO3} on Si, $\lambda_{ex} = 532$ nm.}
\label{fig:mooxch}
\end{figure}
The Raman spectrum of the as-synthesized specimen also closely matches \ce{MoO3} features in previous studies.\cite{Dixit1986,Silveira2012} During m-Raman measurement, the laser spot was carefully focused onto the plates and several inspections on different positions were observed to ensure the reproductivity of spectra data. As shown in Fig.~\ref{fig:moram}, 14 distinct bands were well resolved. The 284 \si{cm^{-1}} peak represents the wagging mode for double bond \ce{O=Mo=O}. The 337 and 380  \si{cm^{-1}} peaks are assigned to \ce{O-Mo-O} bending and scissoring modes. The 199 \si{cm^{-1}} peak and two other weaker peaks at 218 and 247 \si{cm^{-1}} represent \ce{O=Mo=O} $B_{2g}$ twist, $A_g$ chain mode and \ce{O=Mo=O} $B_{3g}$ twist mode, respectively. The 667 \si{cm^{-1}} peak is assigned to triply coordinated oxygen stretching model resulting from edge-shared oxygen in common to three octahedral. The 819 \si{cm^{-1}} peak is from doubly coordinated oxygen stretching mode arising from corner-shared oxygen between two octahedral. The 996 \si{cm^{-1}} peak comes from unshared oxygen stretching mode.\cite{Siciliano2009} The assignment is summarized in Table~\ref{tab:moram}.
% raman assign
\begin{table}[htb]
\centering
\caption[Experimental Raman peaks assignment of \ce{MoO3} on Si]{Experimental Raman peaks assignment of \ce{MoO3} on Si.\cite{Eda1992,Siciliano2009}}\label{tab:moram}
\begin{tabular}{llcll}
\toprule
this work(\si{cm^{-1}}) & Sym.  &    & Assignment &   \\
\midrule
117      & $B_{2g}$    &           & $T_c$  & RCM\textsuperscript{\emph{a}}  \\
129      & $B_{3g}$    &           & $T_c$  & RCM  \\
158      & $A_g/B_{1g}$&           & $T_b$  & RCM  \\
199      & $B_{2g}$    & $\tau$    & \ce{O=Mo=O}  & twist  \\
218      & $A_g$       &           & $R_c$     & RCM  \\
247      & $B_{3g}$    & $\tau$    & \ce{O=Mo=O}  & twist  \\
284      & $B_{2g}$    &           & \ce{O=Mo=O}  & wag  \\
292      & $B_{3g}$     & $\delta$ & \ce{O=Mo=O}  & wag  \\
337      & $A_g,B_{1g}$ & $\delta$ & \ce{O-Mo-O} & bend  \\
380      & $B_{1g}$     & $\delta$ & \ce{O-Mo-O}  & scissor  \\
474      & $A_g$        & $\nu_{as}$ & \ce{O-Mo-O}  & stretch,bend  \\
667      & $B_{2g},B_{3g}$ & $\nu_{as}$  & \ce{O-Mo-O}  & stretch  \\
819      & $A_g$        & $\nu_{as}$  & \ce{O=Mo}  & stretch  \\
996      & $A_g$         & $\nu_{as}$  & \ce{O=Mo}  & stretch  \\
\bottomrule
\end{tabular}

@@

R is molar gas constant (8.315 \si{\joule\per mol\per K}), and T is temperature in K.
\end{table}
It is worth mentioning that the gradient of Gibbs free enthalpy overruled the concentration of a particular species, and higher \ce{OH-} contents tend to reduce Na diffusivity.\cite{Materials2012} The substrates used in this work are glass and ITO/glass; the relevant parameters are as following:
\begin{itemize}
\item dimension: $25\times10\times1$ mm
\item density: 2.567 \si{g\per cm^3}
\item Na concentration: 0.01 \si{mol\per cm^3}
\item $D$: $1.1\times10^{-7}$ \si{cm^2\per\second}
\end{itemize}
Substituting these values into Eq.~\ref{eq:nadiff}, the net flux $J$ is estimated as
\begin{align}
J = -D \frac{\Delta C}{\Delta x} = 2.0\times 10^{-8} \si{mol\per cm^2\per\second}.
\end{align}
In typical growth of 2 h, the net amount of Na diffusing out of substrate is then $1.44\times10^{-4}$ mol, which is about 10\% of total Na ions in the glass substrates. The diffusion length $\sqrt{Dt}$ is 190 $\mu$m. Notice this result overestimates since the flux will reduce gradually. Meanwhile the molar amount of \ce{NaOH} applied on Si substrate is about $5\times10^{-7}$ mol. Considering the adjusted ratio, Na contents should be much more when using glass substrate than when using NaOH-Si substrate. Another important factor is the evaporation of sodium molybdates. However, few report could be found in literature. Only one was reported by \citeauthor{Kazenas2010}.\cite{Kazenas2010} The partial pressure of \ce{Na2MoO4} is calculated to be 0.2 mTorr at 800 \si{\degreeCelsius} and $3.5\times 10^{-3}$ mTorr at 670 \si{\degreeCelsius}.\footnote{$\log P(atm)= -13794/T + 6.19$}

>>>>

As shown in Fig.~\ref{fig:mooxch}, the crystal structure and phase of the as-synthesized specimen were examined by XRD and Raman. The XRD pattern (Fig.~\ref{fig:moxrd}) is readily indexed to the orthorhombic phase of \ce{MoO3} (ICDD PDF 05-0508, \emph{a}=3.9628 \AA, \emph{b}=13.855 \AA, \emph{c}=3.6964 \AA). The space group is $D_{2h}^{16}(Pbnm)$. This crystal structure is indeed a unique example among transition metal oxides, representing a transitional stage between tetrahedra and octahedral coordination.\cite{Itoh2001a} The strongest peak index is (110), suggesting the orientation of \ce{MoO3} is not parallel to the substrate, which is consistent with the morphology displayed in Fig.~\ref{fig:mosem1}. In contrast, a different XRD peak pattern is observed in Sec.~\ref{sec:nasi}, where the catalytic growth occurs.
% xrd raman
% 081113 sample
\begin{figure}[htb]
\centering
\subfloat[]{\label{fig:moxrd}\includegraphics[width=0.45\textwidth]{xrd_moo3}}\hspace{0.04\textwidth}
\subfloat[]{\label{fig:moram}\includegraphics[width=0.45\textwidth]{raman_moo3}}
\caption[Crystalline phase characterization of \ce{MoO3} on Si]{Crystalline phase characterization of \ce{MoO3} on Si: (a) XRD pattern and (b) Raman spectrum of typical \ce{MoO3} on Si, $\lambda_{ex} = 532$ nm.}
\label{fig:mooxch}
\end{figure}
The Raman spectrum of the as-synthesized specimen also closely matches \ce{MoO3} features in previous studies.\cite{Dixit1986,Silveira2012} During m-Raman measurement, the laser spot was carefully focused onto the plates and several inspections on different positions were observed to ensure the reproductivity of spectra data. As shown in Fig.~\ref{fig:moram}, 14 distinct bands were well resolved. The 284 \si{cm^{-1}} peak represents the wagging mode for double bond \ce{O=Mo=O}. The 337 and 380  \si{cm^{-1}} peaks are assigned to \ce{O-Mo-O} bending and scissoring modes. The 199 \si{cm^{-1}} peak and two other weaker peaks at 218 and 247 \si{cm^{-1}} represent \ce{O=Mo=O} $B_{2g}$ twist, $A_g$ chain mode and \ce{O=Mo=O} $B_{3g}$ twist mode, respectively. The 667 \si{cm^{-1}} peak is assigned to triply coordinated oxygen stretching model resulting from edge-shared oxygen in common to three octahedral. The 819 \si{cm^{-1}} peak is from doubly coordinated oxygen stretching mode arising from corner-shared oxygen between two octahedral. The 996 \si{cm^{-1}} peak comes from unshared oxygen stretching mode.\cite{Siciliano2009} The assignment is summarized in Table~\ref{tab:moram}.
% raman assign
\begin{table}[htb]
\centering
\caption[Experimental Raman peaks assignment of \ce{MoO3} on Si]{Experimental Raman peaks assignment of \ce{MoO3} on Si.\cite{Eda1992,Siciliano2009}}\label{tab:moram}
\begin{tabular}{llcll}
\toprule
this work(\si{cm^{-1}}) & Sym.  &    & Assignment &   \\
\midrule
117      & $B_{2g}$    &           & $T_c$  & RCM\textsuperscript{\emph{a}}  \\
129      & $B_{3g}$    &           & $T_c$  & RCM  \\
158      & $A_g/B_{1g}$&           & $T_b$  & RCM  \\
199      & $B_{2g}$    & $\tau$    & \ce{O=Mo=O}  & twist  \\
218      & $A_g$       &           & $R_c$     & RCM  \\
247      & $B_{3g}$    & $\tau$    & \ce{O=Mo=O}  & twist  \\
284      & $B_{2g}$    &           & \ce{O=Mo=O}  & wag  \\
292      & $B_{3g}$     & $\delta$ & \ce{O=Mo=O}  & wag  \\
337      & $A_g,B_{1g}$ & $\delta$ & \ce{O-Mo-O} & bend  \\
380      & $B_{1g}$     & $\delta$ & \ce{O-Mo-O}  & scissor  \\
474      & $A_g$        & $\nu_{as}$ & \ce{O-Mo-O}  & stretch,bend  \\
667      & $B_{2g},B_{3g}$ & $\nu_{as}$  & \ce{O-Mo-O}  & stretch  \\
819      & $A_g$        & $\nu_{as}$  & \ce{O=Mo}  & stretch  \\
996      & $A_g$         & $\nu_{as}$  & \ce{O=Mo}  & stretch  \\
\bottomrule
\end{tabular}

@@

R is molar gas constant (8.315 \si{\joule\per mol\per K}), and T is temperature in K.
\end{table}

The substrates used in this work are glass and ITO/glass; the relevant parameters are as following:
\begin{itemize}
\item dimension: $25\times10\times1$ mm
\item density: 2.567 \si{g\per cm^3}
\item Na concentration: 0.01 \si{mol\per cm^3}
\item $D$: $1.1\times10^{-7}$ \si{cm^2\per\second}
\end{itemize}
Substituting these values into Eq.~\ref{eq:nadiff}, the net flux $J$ is estimated as
\begin{align}
J = -D \frac{\Delta C}{\Delta x} = 2.0\times 10^{-8} \si{mol cm^{-2}s^{-1}}.
\end{align}
In typical growth of 2 h, the net amount of Na diffusing out of substrate is then $1.44\times10^{-4}$ mol, which is about 10\% of total Na ions in the glass substrates. The diffusion length $\sqrt{Dt}$ is 190 $\mu$m. Notice this result overestimates since the flux will reduce gradually. Meanwhile the molar amount of \ce{NaOH} applied on Si substrate is about $5\times10^{-7}$ mol. Considering the adjusted ratio, Na contents should be much more when using glass substrate than when using NaOH-Si substrate. Another important factor is the evaporation of sodium molybdates. However, few report could be found in literature. Only one was reported by \citeauthor{Kazenas2010}.\cite{Kazenas2010} The partial pressure of \ce{Na2MoO4} is calculated to be 0.2 mTorr at 800 \si{\degreeCelsius} and $3.5\times 10^{-3}$ mTorr at 670 \si{\degreeCelsius}.\footnote{$\log P(atm)= -13794/T + 6.19$}

### 2015-02-05 ch-tms/tmspart.tex
main text fine tuned

\section{Introduction}
\subsection{Properties and Applications of WS$_2$}
Tungsten disulfide (\ce{WS2}) is a group VI dichalcogenide semiconductor compound. The molecular weight is 249.97 \si{g\per \mole}. Almost all natural \ce{WS2} belongs to P63/mmc space group (2H-\ce{WS2}), where $a$ is 3.153 \si{\angstrom}, $c$ is 12.323 \si{\angstrom} (PDF 04-003-4478). Two other crystal structures were found in man-made \ce{WS2}, i.e., 1T and 3R, where 3R can be prepared by bromine (Br) chemical vapor transport (CVT) method \cite{Schutte1987} and 1T was generally found in alkaline intercalated \ce{WS2}.\cite{Yang1996a, Enyashin2011} As a reference, the lattice dimensions are summarized in Table~\ref{tab:ms2lattice}.
%lattice
\begin{table}[htb]
\centering
\caption{Lattices dimension of \ce{MS2}}\label{tab:ms2lattice}
\begin{tabular}{lccr}
\toprule
         &  & 2H-\ce{MoS2}\cite{Coehoorn1987,Ataca2012} & 2H-\ce{WS2}\cite{Albe2002,Schutte1987} \\
\midrule
Lattice constant & a(\AA) & 3.1604 & 3.171 \\
                 & c(\AA) & 12.295 & 12.359 \\
Within \ce{MS2} layer & M-3S (\AA)& 2.37  & 2.405   \\
                      & S-1S (\AA)& 3.11  & 3.14   \\
Between \ce{MS2} layer& S-3S (\AA)&   & 3.53   \\
\bottomrule
\end{tabular}
\end{table}

@@

% CVD TMDC
\begin{landscape}
\begin{table}[htb]
\centering
\caption{Summary of TMDC few layer growth methods}\label{tab:tmsgrowth}
{\footnotesize
\begin{tabular}{lp{2.5in}p{4.5in}}
\toprule
TMDC  &  precursor & growth condition (default temperature unit \si{\degreeCelsius}) \\
\midrule
\ce{MoS2} films \cite{Lee1994,Endler1999} & \ce{MoCl5}, \ce{H2S} & 1 kPa, temperature: 400-550 \si{\degreeCelsius}, 100/10/2.5 sccm for Ar, \ce{H2S} and \ce{MoCl5} flow\\
\addlinespace[0.5em]
\ce{MoS2} FL \cite{Zhan2012} & 1-5 nm Mo films on \ce{SiO2}, Sulfur & purging, RT-550@30 min, 550-750@90 min and hold for 10 min. Mo coating on Si did not work.\\
\ce{MoS2} FL \cite{Lin2012,Wang2013} & 4 nm \ce{MoO3} coating on sapphire  & reduced to \ce{MoO2} in \ce{H2} and Ar at 500 \si{\degreeCelsius}, sulfurization at 850-1000 \si{\degreeCelsius} \\
\addlinespace[0.5em]
\ce{MoS2} FL \cite{Liu2012a} & \ce{(NH4)2MoS4} in DMF solution transport by Ar bubbler or dip-coating onto subs &  annealing under Ar or Ar + Sulfur, total pressure 0.2-2 Torr, \\
 \addlinespace[0.5em]
\ce{MoS2} FL \cite{Wu2013} & \ce{MoS2} powder & Ar flow, 900 \si{\degreeCelsius} heating, pressure 20 Torr, 650 \si{\degreeCelsius} growth\\
 \addlinespace[0.5em]
\ce{MoS2} FL \cite{Mann2013,Najmaei2013,Ji2013} Rice & \ce{MoO3} powders or ribbons, Sulfur & Ar flow, 530-850 \si{\degreeCelsius}, total pressure 0.2-2 Torr, 5-30 min, mica or \ce{SiO2}-Si\\
 \addlinespace[0.5em]
\ce{MoS2} FL \cite{Lee2012b,Ling2014} & 18mg \ce{MoO3} powders, Sulfur,various seeding promoter on sub & 5sccm Ar, 650 \si{\degreeCelsius}, 3 min growth, atmospheric pressure, quick cooling\\

@@

\begin{figure}[htb]
\centering
\includegraphics[width=0.7\textwidth]{ws2_ramsch}
\caption[\ce{MS2} vibration symmetry]{\ce{MS2} vibration symmetry in bulk and monolayer, adopted from Ref.\cite{Ghorbani-asl}}
\label{fig:ws2ramsch}
\end{figure}

>>>>

\section{Introduction}
\subsection{Properties and Applications of WS$_2$}
Tungsten disulfide (\ce{WS2}) is a group VI dichalcogenide semiconductor compound. The molecular weight is 249.97 \si{g\per \mole}. Almost all natural \ce{WS2} belongs to P63/mmc space group (2H-\ce{WS2}), where $a$ is 3.153 \si{\angstrom}, $c$ is 12.323 \si{\angstrom} (PDF 04-003-4478). Two other crystal structures were found in man-made \ce{WS2}, i.e., 1T and 3R, where 3R can be prepared by bromine (Br) chemical vapor transport (CVT) method \cite{Schutte1987} and 1T was generally found in alkaline intercalated \ce{WS2}.\cite{Yang1996a, Enyashin2011} As a reference, the lattice dimensions are summarized in Table~\ref{tab:ms2lattice}.
%lattice
\begin{table}[htb]
\centering
\caption{Lattices dimension of \ce{MS2}}\label{tab:ms2lattice}
\begin{tabular}{lccr}
\toprule
         &  & 2H-\ce{MoS2}\cite{Coehoorn1987,Ataca2012} & 2H-\ce{WS2}\cite{Albe2002,Schutte1987} \\
\midrule
Lattice constant & a(\AA) & 3.1604 & 3.171 \\
                 & c(\AA) & 12.295 & 12.359 \\
Within \ce{MS2} layer & M-3S (\AA)& 2.37  & 2.405   \\
                      & S-1S (\AA)& 3.11  & 3.14   \\
Between \ce{MS2} layer& S-3S (\AA)& NA  & 3.53   \\
\bottomrule
\end{tabular}
\end{table}

@@

% CVD TMDC
\begin{landscape}
\begin{table}[htb]
\centering
\caption{Summary of TMDC few layer growth methods}\label{tab:tmsgrowth}
{\footnotesize
\begin{tabular}{lp{2.5in}p{4.5in}}
\toprule
TMDC  &  precursor & growth condition (default temperature unit \si{\degreeCelsius}) \\
\midrule
\ce{MoS2} films \cite{Lee1994,Endler1999} & \ce{MoCl5}, \ce{H2S} & 1 kPa, temperature: 400-550 \si{\degreeCelsius}, 100/10/2.5 sccm for Ar, \ce{H2S} and \ce{MoCl5} flow\\
\addlinespace[0.5em]
\ce{MoS2} FL \cite{Zhan2012} & 1-5 nm Mo films on \ce{SiO2}, Sulfur & purging, RT-550@30 min, 550-750@90 min and hold for 10 min. Mo coating on Si did not work.\\
\ce{MoS2} FL \cite{Lin2012,Wang2013} & 4 nm \ce{MoO3} coating on sapphire  & reduced to \ce{MoO2} in \ce{H2} and Ar at 500 \si{\degreeCelsius}, sulfurization at 850-1000 \si{\degreeCelsius} \\
\addlinespace[0.5em]
\ce{MoS2} FL \cite{Liu2012a} & \ce{(NH4)2MoS4} in DMF solution transport by Ar bubbler or dip-coating onto subs &  annealing under Ar or Ar + Sulfur, total pressure 0.2-2 Torr, \\
 \addlinespace[0.5em]
\ce{MoS2} FL \cite{Wu2013} & \ce{MoS2} powder & Ar flow, 900 \si{\degreeCelsius} heating, pressure 20 Torr, 650 \si{\degreeCelsius} growth\\
 \addlinespace[0.5em]
\ce{MoS2} FL \cite{Mann2013,Najmaei2013,Ji2013} & \ce{MoO3} powders or ribbons, Sulfur & Ar flow, 530-850 \si{\degreeCelsius}, total pressure 0.2-2 Torr, 5-30 min, mica or \ce{SiO2}-Si\\
 \addlinespace[0.5em]
\ce{MoS2} FL \cite{Lee2012b,Ling2014} & 18mg \ce{MoO3} powders, Sulfur,various seeding promoter on sub & 5sccm Ar, 650 \si{\degreeCelsius}, 3 min growth, atmospheric pressure, quick cooling\\

@@

\begin{figure}[htb]
\centering
\includegraphics[width=0.7\textwidth]{ws2_ramsch}
\caption[\ce{MS2} vibration symmetry]{\ce{MS2} vibration symmetry in bulk and monolayer, reproduced from Ref.\cite{Ghorbani-Asl2013}}
\label{fig:ws2ramsch}
\end{figure}

### 2015-02-05 ch-wox/ch-wox.tex
core shell chapter revised
images replaced, fine tune
main text fine tuned

\subsection{Non-seeded growth}

@@

\section{Results and Discussion on 1D Nanowire Growth}
\subsection{Tungsten Oxides: Impurities and Residual Effects}\label{sec:nawox}

@@

The \ce{Na5W14O44} phase was further confirmed by a XRD scanning from 4 to 10 degree in $2\theta/\Omega$ configuration. As shown in Fig.~\ref{fig:naxrdlow}, two peaks at 4.84$^{\circ}$ and 9.65$^{\circ}$ were well resolved, corresponding a lattice spacing of 18.25 and 9.16 \si{\angstrom}, respectively. This compares favorably with both HRTEM analysis (Fig.~\ref{fig:nawoxtem}e) and ICDD PDF 04-012-4449 database reference. 
%061212 sample
\begin{figure}[htb]
\centering
\includegraphics[width=0.5\textwidth]{naxwo_xrd_low}
\caption{Low angle scan of XRD pattern on the as-grown sodium tungsten oxide sample}
\label{fig:naxrdlow}
\end{figure}

@@

Understanding the oxidation of tungsten powder is the key to obtain high yield in seeded growth. Oxidation of tungsten have been investigated under diverse conditions, such as at elevated temperature (\textgreater 1100 \si{\degreeCelsius}) and oxygen pressure on the order of Torr,\cite{Base1965} and at temperatures ranging from 20 to 500 \si{\degreeCelsius} under atmosphere pressure.\cite{Warren1996} \ce{WO_x} NWs were readily found when tungsten (foil, wire, or powder) is oxidized under various conditions.\cite{Zhu1999,Karuppanan2007,Hsieh2010} However the study on tungsten powder oxidation behavior between intermediate temperature range and under low pressure is still rare. This thesis studied the oxidation of tungsten powders with diverse size within temperature range from 500 to 1000 \si{\degreeCelsius} and under several mTorr oxygen partial pressure. It was illustrated that using tungsten powder as seed is an economic approach to obtain high yield of \ce{WO3} nanowires at relatively lower temperature. It was also demonstrated that there was an optimal tungsten powder size under current experimental conditions for seeded growth. This observation will provide some insight on the role of tungsten powder as source material in CVD growth of \ce{WO_x}.

>>>>

\subsection{Non-seeded growth}\label{sec:woxnonseed}

@@

\section{Results and Discussion on 1D WO$_3$ Nanowire}
\subsection{Tungsten Oxides: Impurities and Residual Effects}\label{sec:nawox}

@@

The \ce{Na5W14O44} phase was further confirmed by a XRD scanning from 4 to 10 degree in $2\theta/\Omega$ configuration. As shown in Fig.~\ref{fig:naxrdlow}, two peaks at 4.84$^{\circ}$ and 9.65$^{\circ}$ were well resolved, corresponding a lattice spacing of 18.25 \si{\angstrom} and 9.16 \si{\angstrom}, respectively. This compares favorably with both HRTEM analysis (Fig.~\ref{fig:nawoxtem}e) and ICDD PDF 04-012-4449 database reference. 
%061212 sample
\begin{figure}[htb]
\centering
\includegraphics[width=0.5\textwidth]{naxwo_xrd_low}
\caption{Low angle scan of XRD pattern on the as-grown sodium tungsten oxide sample}
\label{fig:naxrdlow}
\end{figure}

@@

Understanding the oxidation of tungsten powder is the key to obtain high yield in seeded growth. Oxidation of tungsten have been investigated under diverse conditions, such as at elevated temperature (\textgreater 1100 \si{\degreeCelsius}) and oxygen pressure on the order of Torr,\cite{Gulbransen1960} and at temperatures ranging from 20 to 500 \si{\degreeCelsius} under atmosphere pressure.\cite{Warren1996} \ce{WO_x} NWs were readily found when tungsten (foil, wire, or powder) is oxidized under various conditions.\cite{Zhu1999,Karuppanan2007,Hsieh2010} However the study on tungsten powder oxidation behavior between intermediate temperature range and under low pressure is still rare. This thesis studied the oxidation of tungsten powders with diverse size within temperature range from 500 to 1000 \si{\degreeCelsius} and under several mTorr oxygen partial pressure. It was illustrated that using tungsten powder as seed is an economic approach to obtain high yield of \ce{WO3} nanowires at relatively lower temperature. It was also demonstrated that there was an optimal tungsten powder size under current experimental conditions for seeded growth. This observation will provide some insight on the role of tungsten powder as source material in CVD growth of \ce{WO_x}.
